---
title: "`r desc::desc_get('Title', '..')`"
author: "Hao Ye"
institute: "Health Science Center Libraries, University of Florida"
date: "(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    seal: false
    fig_caption: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#09274B",
  base_font_size = "32px", 
  header_h1_font_size = "2.0rem",
  header_h2_font_size = "1.5rem",
  header_h3_font_size = "1.25rem", 
  header_background_content_padding_top = "2rem", 
  header_font_google = google_font("Lato"),
  text_font_google   = google_font("Montserrat", "300", "300i", "500"),
  code_font_google   = google_font("Source Code Pro", "300", "500"), 
  extra_css = list("p" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "ul" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "li" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "pre" = list("margin-top" = "0.5em", 
                              "margin-bottom" = "0.5em"), 
                   ".small" = list("font-size" = "80%"), 
                   ".tiny" = list("font-size" = "50%")), 
  link_color = "#339944"
)
```
class: inverse, center, middle

# `r desc::desc_get('Title', '..')`
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$institute`
### (updated: `r Sys.Date()`)

---
# Motivations

* You would like a professional-looking website to present yourself.
* You don't want to spend time/money designing something completely custom.
* You want to use or learn github / blogdown.
* You want to make blogposts using R Markdown.

---
# Prerequisites

This lesson assumes you:
`r gsub("\n ", "\n", desc::desc_get("prerequisites"))`

Such as via `r desc::desc_get("priorCourse")`

---
# Learning Outcomes

By the end of the workshop, participants will be able to:

`r gsub("\n ", "\n", desc::desc_get("learningOutcomes"))`

---
class: inverse, center, middle

# Setup

---
# Required Packages

```{r, eval = FALSE}
install.packages(c("usethis"
                   "blogdown", 
                   "renv"))
```

These packages and their included dependencies will have all the tools that we need to get started.

---
# Git and RStudio

RStudio is not required, but does make some steps easier, so I strongly recommend it.

If you have not yet configured Git and GitHub for use from within RStudio, check out these guides:
* ["Happy Git and GitHub for the useR"](https://happygitwithr.com/)
* ["Managing Git(Hub) Credentials"](https://usethis.r-lib.org/articles/git-credentials.html)

---
# Install Hugo

Hugo is a static site generator that we will use. This code from the blogdown package will install the latest version and make it available to us.

```{r, eval = FALSE}
blogdown::install_hugo()
```

---
class: inverse, center, middle

# Creating a new site

---
# Choose a name

We are going to use GitHub Pages to host our website.

The address will be https://{username}.github.io/{repo}
  e.g for my username `ha0ye` and repo `my-site`, the eventual website address will be https://ha0ye.github.io/my-site/

You can also host at https://{username}.github.io/ ; choose `{username}.github.io` as the repo name.

---
# New RStudio Project

1. Open RStudio.
2. `File` -> `New Project`
3. Select `New Directory`
4. Use the name previously chosen, set the local directory, and `Create Project`.

---
# Create Blogdown Site

```{r, eval = FALSE}
blogdown::new_site(theme = "hugo-apero/hugo-apero", 
                   format = "toml",
                   sample = FALSE,
                   empty_dirs = TRUE)
```

---
# Set `baseURL`

Open `config.toml`.

There are a number of configuration options here.
Right now, set baseURL to the eventual URL of your site.

For example:
```
baseURL = "https://ha0ye.github.io/blogdown-demo"
```

---
# Activate renv

The `renv` package will capture all the needed packages to build our website and record this information in configuration files that GitHub will use.

```{r, eval = FALSE}
renv::init()
renv::snapshot()
```

---
# Setup GitHub Actions

We need to give GitHub instructions on how to build our website, and there is a premade script for us to use.

```{r, eval = FALSE}
usethis::use_github_action("blogdown")
```

---
# Commit and Push

These commands will enable Git for this project, and then push it to a new repo on GitHub.

```{r, eval = FALSE}
usethis::use_git()
usethis::use_github()
```

---
class: middle, center

# Demo

---

 
---
# Thanks

* Let me know what content you'd like to see
* Contact me for additional questions or consultation requests!
* Check back in on the libguide for more modules and contact info:
  - https://guides.uflib.ufl.edu/reproducibility
